% !TeX spellcheck = en_GB
\chapter*{Abstract}


Besides being a mathematically interesting topic on its own, subfactors have also attracted the attention of physicists, since there is a conjectured correspondence between these and Conformal Field Theories (CFTs). 
Although there is quite a persuasive body of evidence for this conjecture, there are some gaps: there exists a set of exceptional subfactors with no known counterpart CFT. Hence, it is necessary to develop new techniques for building a CFT from a subfactor. Here, it is useful to study the underlying mathematical structure in more detail: The even parts of every subfactor give rise to two Unitary Fusion Categories (UFCs), and it is a promising direction to study quantum spin systems constructed from these categories to find a connection to CFTs. 

The simplest example that requires new techniques for building a CFT is the Haagerup subfactor, since it is the smallest subfactor with index larger than $4$. In this thesis, we investigate the question whether there is a CFT corresponding to the Haagerup subfactor via lattice models in one and two dimensions. The first task here is to find the $F$-symbols of the fusion category since these are crucial ingredients for the construction of a physical model in all of the models we consider in this thesis. We then investigate the following models:
\begin{enumerate}
	\item The golden chain model, which is a one-dimensional spin chain whose ground state can be investigated in order to obtain information about the hypothetical CFT (such as the central charge).
	\item Quantum spin chains (such as the golden chain model) with defects. The construction of the vertices of the defect chain gives insight into a possible way to construct a Unitary Modular Tensor Category (UMTC) via the so-called annular category.
	\item The Levin-Wen model, which is a two-dimensional lattice model with an exactly solvable Hamiltonian that gives rise to a topological quantum field theory. Most interestingly for us, the excitations of the system yield a UMTC.
\end{enumerate}

We find that there is no evidence for a corresponding CFT from the investigation of the UFCs directly and it is necessary to expand these studies to the corresponding UMTC, which can, for instance, be obtained via the excitations of the Levin-Wen model.


\hspace{10pt}

\noindent
\textit{Keywords:} Conformal field theory, anyon chains, fusion categories