\chapter*{Acknowledgements}



%\textbf{Supervision}: Tobias J. Osborne, Reinhard Werner

First, I would like to thank my supervisor Tobias Osborne for introducing me to a fascinating area at the intersection of mathematics and physics, for guiding me through this thesis, and for always sharing valuable advice. I would also like to thank Reinhard Werner for his feedback and advice and for sharing all the interesting stories at lunch at the Mensa. A special thanks goes also to all (past and current) members of the Quantum Information Theory group in Hanover. You have made the day to day process of research a pleasure, especially on days where one of you brought cake to the institute!

%\textbf{Collaborations}: Jacob Bridgeman, Alexander Hahn, Kerstin Beer, Dmytro Bondarenko, Terry Farrelly, René Schwonnek, Cain Edie-Michell, Charles Lim

During my time as a PhD student, I had the opportunity to visit many great places and to work with a lot of great, inspiring people. I would like to thank Kerstin Beer, Jacob Bridgeman, Dmytro Bondarenko, Cain Edie-Michell, Terry Farrelly, Alexander Hahn, Charles Lim, René Schwonnek, and Deniz Stiegemann for sharing their knowledge and passion with me and for the collaboration on several interesting projects. I would especially like to thank Charles Lim and René Schwonnek for giving me the possibility to visit Singapore and for having me at the CQT. I also especially thank Alexander Hahn for many helpful discussions on all aspects of fusion categories and the joint work on several projects that ended up being a part of this thesis.

%\textbf{Proofreading}: Alexander Hahn, Cain Edie-Michell, Jacob Bridgeman, Ashley Milsted, Thomas Cope, Christin Schridde, Alexander Kranz

There are many people who granted helpful advice and valuable comments on earlier versions of this thesis, who have found several typos and have helped to bring this thesis in its final form: Many thanks to Jacob, Tom, Cain, Alexander H., Alexander K., Ashley, and Christin.

%\textbf{Private}: family, Omas, Alex' family, Alex, Louis

%Finally I would like to thank my family for their support, my parents, my brother, and my grandmothers. Even though you have no idea what I am actually doing, you have always supported me and each of you has had a great influence on me in the past years. Without you, this thesis would not have been possible. I would also like to thank my ``second family'', Sophia, Peter, and Louis (the cutest cat in the world and best officemate during the lock down), for supporting me especially in the past year. 
%
%Last but not least, I want to thank Alex. Thanks for you support, your love and your patience.

Besonderer Dank geht auch an meine Familie, meine Eltern, meinen Bruder und meine beiden Großmütter. Auch wenn ihr keine Ahnung habt, was ich eigentlich mache, habt ihr mich immer unterstützt und jeder von euch hatte in den vergangenen Jahren auf die ein oder andere Weise einen großen Einfluss auf mich. Ohne euch wäre diese Doktorarbeit nicht möglich gewesen. Ich möchte mich auch herzlich bei meiner ,,zweiten Familie'', Sophia und Peter, für die Unterstützung im letzten Jahr bedanken! Und natürlich bei Louis, der süßesten Katze und bestem Kollegen in Homeoffice-Zeiten!

Zuletzt möchte ich mich bei Alex bedanken. Danke für deine Unterstützung, Liebe, und Geduld, und dass du mich daran erinnert hast, auch mal Pause zu machen.